### 2011-11-04 doc/manuscript.tex
Just an update.

% FIXME: Remove the followings if you have to when submitting the manuscript.
\let\citep\cite
\let\citet\cite
\providecommand{\tabularnewline}{\\}
\newcommand{\lyxdot}{.}
\@ifundefined{showcaptionsetup}{}{%
 \PassOptionsToPackage{caption=false}{subfig}}
\usepackage{subfig}

@@

\subfloat[]{\includegraphics[scale=0.4]{figures/h3-R-ratio-topology-changing}}

\subfloat[]{\includegraphics[scale=0.4]{figures/h3-R-ratio-not-topology-changing}}

@@

%=============================================================================
% Figure S2. Three population parameters.
\begin{figure}[!ht]
\begin{center}
\subfloat[]{\includegraphics[scale=0.5]{figures/scatter-plot-parameter-1\lyxdot out\lyxdot theta}}

\subfloat[]{\includegraphics[scale=0.5]{figures/scatter-plot-parameter-1\lyxdot out\lyxdot rho}}

\subfloat[]{\includegraphics[scale=0.5]{figures/scatter-plot-parameter-1\lyxdot out\lyxdot delta}}
\end{center}
\caption{
{\bf Three scatter plots of mutation rate, recombination
rate, and average tract length for the blocks.} The plus signs are mean values
for each block. The density of each value for each block is depicted by black
clouds.  The red dashed lines are the global block-length weighted median of the
three parameter estimates.}
\end{figure}
\label{fig:scatter3}
\clearpage{}%
%=============================================================================

>>>>

% FIXME: Remove the followings if you have to when submitting the manuscript.
\let\citep\cite
\let\citet\cite
\providecommand{\tabularnewline}{\\}
\newcommand{\lyxdot}{.}

% \@ifundefined{showcaptionsetup}{}{%
% \PassOptionsToPackage{caption=false}{subfig}}
% \usepackage{subfig}

@@

\includegraphics[scale=0.4]{figures/h3-R-ratio-topology-changing}

\includegraphics[scale=0.4]{figures/h3-R-ratio-not-topology-changing}

@@

%=============================================================================
% Figure S2. Three population parameters.
\begin{figure}[!ht]
\begin{center}
\includegraphics[scale=0.5]{figures/scatter-plot-parameter-1\lyxdot out\lyxdot theta}

\includegraphics[scale=0.5]{figures/scatter-plot-parameter-1\lyxdot out\lyxdot rho}

\includegraphics[scale=0.5]{figures/scatter-plot-parameter-1\lyxdot out\lyxdot delta}
\end{center}
\caption{
{\bf Three scatter plots of mutation rate, recombination
rate, and average tract length for the blocks.} The plus signs are mean values
for each block. The density of each value for each block is depicted by black
clouds.  The red dashed lines are the global block-length weighted median of the
three parameter estimates.}
\end{figure}
\label{fig:scatter3}
\clearpage{}%
%=============================================================================
